Storm surge modelling in the Strait of Georgia

### 2014-10-22 RoughWork/manuscript.tex
Brief overview of the Nov 2006 case

\subsection{An Additional Hindcast: November 16, 2006}

>>>>

\subsection{An Additional Hindcast: November 16, 2006}
An additional storm surge hindcast for November 2006 is provided as another means of assessing model performance and is mentioned briefly here. On November 16, 2006 communities in the Strait of Georgia experienced a strong wind storm with speeds upwards of 20 m/s near Point Atkinson resulting in observed water levels of 5.1 m and a maximum surge amplitude of 83.7 cm. The surge amplitude was lower at the other stations, reaching no more than 68 cm. The model performs reasonably well in this hindcast, Willmott skill scores less greater than 0.94 as outlined in Table \ref{tab:nov2006stat}.  The best match in maximum surge occured at Campbell River 6.2 cm underestimate by the model. The timing of the maximum surge at Campbell River was identical with observations and slightly earlier at the other stations.

\begin{table}[h]
\centering 
\begin{tabular}{|l |c c c c c | c c c c c|} 
\hline 
& \multicolumn{5}{|c|}{Water Level ($\eta$)}        & \multicolumn{5}{|c|}{Residual ($\delta$)} \\ 
\hline 
Location       & $\bar{e}$ (cm) & $\bar{\eta_{o}}$ (m) & $\bar{\eta_{m}}$ (m) & $\gamma^2$ & $WS$   & $\bar{e}$ (cm) & $\bar{\delta_{o}}$ (m) & $\bar{\delta_{m}}$ (m) & $\gamma^2$ & $WS$ \\
\hline 
Point Atkinson &  9.8           &  3.42                & 3.43                 &   0.034    & 0.991  &  7.7           &  0.290                 & 0.247                  &  0.128     & 0.950 \\
Victoria       &  9.1           &  2.16                & 2.11                 &   0.070    & 0.978  &  6.2           &  0.222                 & 0.247                  &  0.171     & 0.946 \\
Patricia Bay   & 10.0           &  2.57                & 2.53                 &   0.049    & 0.985  &  6.6           &  0.235                 & 0.203                  &  0.144     & 0.947 \\
Campbell River & 10.7           &  3.20                & 3.26                 &   0.037    & 0.982  &  6.2           &  0.254                 & 0.236                  &  0.140     & 0.952 \\
\hline 
\end{tabular}
\caption{Evaluation of model performance for the Nov 2006 hindcast.}
\label{tab:nov2006stat} 
\end{table}
